\resumeSubHeadingListStart

\resumeSubItem{ALGOGENE Algo Crypto Trading Challenge 2022 (Global)}{

Candle Patterns, Order Block, RSI, and MFI as trading signals. Variable volume base on past limit orders. Achieved 530M PnL from 1M during Test Round for BTCUSD on the 2018-2020 market. Overall score 86/100. (Currently undergoing Live Market Round)}

\resumeSubItem{Jane Street Electronic Trading Challenge 2022 (Hong Kong)}{

1st runner-up. Built a bot to trade various kinds of stocks including bonds, ADRs, and ETFs by interacting with an emulated exchange. Focused on market-making and arbitrage. High frequency and tick-based. }

\resumeSubItem{J.P. Morgan Code for Good 2022 Challenge (Hong Kong)}{

Developed for Junior Achievement Hong Kong, a job shadowing web app for secondary school students.}

\resumeSubItem{The 6th InnoShow - Faculty of Engineering, The University of Hong Kong}{

Invited to showcase HackOS, an educational offensive cyber-security simulator.}

\resumeSubItem{Cathay Pacific Hackathons 2021}{

Developed a React Native app to display a summary of COVID-19 travel restrictions on an interactive world map.}

\vspace{2pt}
\resumeSubItem{Orientation Workshop @ CUEE 2019 - The Chinese University of Hong Kong}{

Built an image-based object recognition Android app for transportation tools with Deep Learning.}

\vspace{2pt}
\resumeSubItem{STEM Camp 2019 - Shatin Pui Ying College}{

Appointed the Head of STEM Committee, organized a STEM day camp for visiting students from 16 primary schools.}

\vspace{2pt}
\resumeSubItem{EE International Summer Camp 2017 - City University of Hong Kong}{

Developed an Adruino robotic car and Android app for remote control via Bluetooth LE. 2nd runner-up in the camp's concluding Mini Robotic Car Competition.}

\resumeSubHeadingListEnd
