\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand{\companyTitle}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\jobTitle}[2]{
  \item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\jobItem}[2]{
  \item\small{
    \textbf{#1}{: #2}
  }
}

% define KaTeX logo
\makeatletter
\DeclareRobustCommand{\KaTeX}{%
  K\kern -.19em
  {\sbox \z@ T\vbox to\ht \z@ {\hbox{%
  \check@mathfonts
  \fontsize\sf@size\z@
  \selectfont A}%
  \vss}%
}\kern -.15em
\TeX}
\makeatother


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE LEE, Kwok Lam}} & \href{mailto:}{lemuellee.kl@gmail.com}\\
  Computer Science Undergraduate & +852-62382237 \\
  \href{https://github.com/LemuelKL}{github.com/LemuelKL} & \href{https://www.linkedin.com/in/lemuelkl/}{linkedin.com/in/lemuelkl/}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Hong Kong}{ Hong Kong}
      {Bachelor of Engineering in Computer Science}{Sep 2020 - Jun 2024}
      % {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Machine Learning, Applied Deep Learning, Experiential Learning on Artificial Intelligence and Robotics}}}
    \resumeSubheading
        {Shatin Pui Ying College}{Hong Kong}
        {Secondary Education;   1st in ICT, 3rd in Physics}{Sep 2013 - Jun 2020}
        % {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Marjos:} Information and Communications Technology, Physics}}}
  \resumeSubHeadingListEnd


\section{Technical Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Python, C/C\texttt{++}, C\texttt{\#}, JavaScript, TypeScript, JAVA, SQL, \LaTeX, \texorpdfstring{\KaTeX}{KaTeX}}
	\resumeSubItem{Frameworks \& Libraries}{NodeJS, Flask, ReactJS, VueJS, SvelteKit, Quasar, TailwindCSS, Qt, Unity, TensorFlow, PyTorch, OpenCV}
    \resumeSubItem{Platforms \& Tools}{Linux, Bash, MySQL, MongoDB, PostgreSQL, Supabase, Docker, Git, GitHub, Adruino}

\resumeSubHeadingListEnd


\section{Experience}
\begin{itemize}[leftmargin=*]
   
    \companyTitle{Shatin Pui Ying College}{Hong Kong}
        
    \jobTitle{Question Writer \& Programmer (Freelance)}{Jul 2022 - Aug 2022 \& Mar 2021 - Aug 2021}
    \begin{itemize}
        \item \small Authored MCQ templates in JavaScript \& {\KaTeX} for school's e-learning web app \textit{WinMaths}.
            \item \small Templates are based on the 2022 HKDSE Mathematics and the HKDSE Physics syllabus.
    \end{itemize}
        
    \jobTitle{Full Stack Engineer (Freelance)}{Jun 2022 - Aug 2022}
    \begin{itemize}
        \jobItem{Musical E-ticketing System}{Semi-automated order management, seat arrangement, mission control, and bulk mail.}
        \jobItem{Administrative Web Apps}{Developed for exam, lesson, and HKDSE invigilation timetable scheduling.}
    \end{itemize}
        
    \companyTitle{The University of Hong Kong}{Hong Kong}
        
    \jobTitle{Student Teaching Assistant - ENGG1340 Computer Programming II}{Jan 2022 - Jun 2022}
    \jobTitle{Student Teaching Assistant - ENGG1330 Computer Programming I}{Sep 2021 - Dec 2021}
    \begin{itemize}
        \jobItem{ENGG1340}{Tutored a class of 85 on advanced Python programming, Linux shell commands, shell scripts, C/C\texttt{++} programming, and separate compilation techniques.}
        \jobItem{ENGG1330}{Tutored a class of 45 on Python programming, searching and sorting algorithms.}
        \jobItem{Coursework Feedback}{Reviewed assignments according to a marking scheme and gave individual \textbf{video} feedback.}
        \jobItem{Ed \& Moodle}{Guided discussions on learning materials.}
    \end{itemize}
  
\end{itemize}

%-----------PROJECTS-----------------
\vspace{-2pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{3230shell - COMP3230 coursework, a Linux shell (Operating System, Linux)}{

A shell which supports command parsing, program execution, signals handling, multiple background processes, arbitrary number of piped processes and process statistics in any combinations. (Oct 2022)
}

\resumeSubItem{Enoch BRC - a reading challenge for the Bible (Fullstack, PWA, Static Site)}{

A minimalistic Progressive Web App tailored made for a church. Readers read 8 chapters weekly to finish all 1189. Includes leader-board and progress tracker. (Oct 2022)}

\resumeSubItem{CMM - algorithmic cryptocurrency trading (API, Cloud Computing, Data Science)}{

Back-testing suite for ALGOGENE Algo Crypto Trading Challenge 2022 (Global). Market pattern detection and alert via web-hook. Involves APIs of Trading View, Binance, Alpaca, Google Cloud, and Discord. (Jointly developed Oct 2022)}

\resumeSubItem{WinMaths - SPYC's e-learning platform (Functional Programming, Code Generation, Typesetting)}{

Generates random Mathematics and Physics MCQs based on templates written in JavaScript \& HTML \& KaTeX. Incremental development. (Jointly developed and in production since 2019)}

\resumeSubItem{HackOS - COMP3329 coursework, offensive cyber-security simulator game (Unity, Cyber-security)}{

Participating project of the 6th InnoShow held by the Faculty of Engineering, The University of Hong Kong. Sandbox experience with pruned replicas of nmap, ssh, hydra, and an array of UNIX-like commands. (May 2022)}

\resumeSubItem{RNA Fighter - terminal-based puzzle-solving game}{

Terminal game with colored text user-interface. Player race to enter mirrored RNA sequences to defuse viruses. Implemented text-based dialogues, scroll view, page navigation, and in-place buffer update. Built with Ncurses and C++. (May 2021)}


\resumeSubItem{Duckietown Tesla - COMP3414 coursework (Computer Vision, Reinforced Learning, Self-driving)}{

Built for Duckietown using (modified) Deep Deterministic Policy Gradient with Actor \& Critic networks. (Dec 2020)}


\resumeSubItem{Bubble Sheet OMR - GUI program for image-based MCQ options recognition (E-learning, OMR)}
{

Simple GUI program written in Qt to detect MCQ options given a bubble sheet pdf. Coordinates can be exported for automatic marking purpose. Supports fully automatic detection, and fine manual adjustments. Multi-threaded. (Jun 2019)}

\resumeSubItem{Real-time Room Status System - school-wide room status monitoring system (LAMP, RFID)}{

Developed and used for STEM Camp 2018 \& 2019 at Shatin Pui Ying College. Students from 16 primary schools could view booth/room statuses on iPads, and check in \& out by tapping RFID cards. (Apr 2019)}


\resumeSubItem{SLMS - school library management system (SQLite, GUI)}{

Developed with Qt and SQLite, a GUI program that provides CRUD functionalities to common library administration, such as book categorization, borrow/return management, mass book record import, barcode scanning, and overdue alert. Object-oriented and separately compiled. (May 2019)}


\resumeSubItem{Contact List Manager - terminal-based contact list manager}{

Simple terminal application with colored text user-interface. Provides CRUD functionalities to manage contacts with multiple fields. Uses simple hashing algorithms for authentication. Built with Windows API and C++. (May 2018)}
\resumeSubHeadingListEnd

% ACTIVITIES
\vspace{2pt}
\section{Activities}
\resumeSubHeadingListStart
% \resumeSubItem{PwC HackaDay 2022}{

% Built a customizable data lake using cloud technologies.}

\resumeSubItem{ALGOGENE Algo Crypto Trading Challenge 2022 (Global)}{

Achieved a PnL of over 530M with starting capital of 1M during  the Test Round for BTCUSD on the 2018-2020 market. Overall score 86/100. (Currently undergoing Live Market Round)}

\resumeSubItem{Jane Street Electronic Trading Challenge 2022 (Hong Kong)}{

1st runner-up. Built a bot to trade various kinds of stocks including bonds, ADRs, and ETFs by interacting with an emulated exchange. Focused on market-making and arbitrage. High frequency and tick-based. }

\resumeSubItem{J.P. Morgan Code for Good 2022 Challenge (Hong Kong)}{

Developed for Junior Achievement Hong Kong, a job shadowing web app for secondary school students.}

\resumeSubItem{The 6th InnoShow - Faculty of Engineering, The University of Hong Kong}{

Invited to showcase COMP3329 Computer Game Design and Programming coursework HackOS, an educational offensive cyber-security simulator.}

\resumeSubItem{Cathay Pacific Hackathons 2021 - Cathay Pacific}{

Developed a React Native app to display a summary of COVID-19 travel restrictions by tapping an origin \& destination on a world map.}

\vspace{2pt}
\resumeSubItem{Orientation Workshop @ CUEE 2019 - The Chinese University of Hong Kong}{

Built an image-based object recognition Android app for transportation tools with Deep Learning.}

\vspace{2pt}
\resumeSubItem{STEM Camp 2019 - Shatin Pui Ying College}{

Appointed the Head of STEM Committee, organized a STEM day camp for visiting students from 16 primary schools.}

\vspace{2pt}
\resumeSubItem{EE International Summer Camp 2017 - City University of Hong Kong}{

Developed an Adruino robotic car and Android app for remote control via Bluetooth LE. 2nd runner-up in the camp's concluding Mini Robotic Car Competition.}
\resumeSubHeadingListEnd

\end{document}