\documentclass{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\renewcommand*\arraystretch{1.3}
\newcommand{\jobTitle}[3]{
    \vspace{0.3cm}
    \begin{tabular*}{1\textwidth}{||l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2\\
        #3 &
    \end{tabular*}
}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]
\setlength\parindent{0em}

\begin{document}
\begin{center}
  \textbf{\LARGE Lemuel LEE Kwok Lam}

  \vspace{0.2cm}
  Computer Science Penultimate Year Student

  Self-motivated and highly adaptable with a passion for technology and a desire to learn.

  \vspace{0.2cm}
  \begin{tabular}{ c c c }
    London \& Hong Kong & \href{mailto:lemuellee.kl@gmail.com}{lemuellee.kl@gmail.com} & +44 07597243186 \& +852 62382237
  \end{tabular}

  \vspace{0.2cm}
  \begin{tabular}{ c c c c }
    \faGlobe \space \href{https://lemuellee.com}{lemuellee.com} &
    \faLinkedin \space \href{https://linkedin.com/in/lemuelkl}{linkedin.com/in/lemuelkl} &
    \faGithub \space \href{https://www.github.com}{github.com/LemuelKL}
  \end{tabular}
\end{center}

\section{EXPERIENCE}

\jobTitle
{Question Writer \& Programmer}
{Jul 2022 --- Aug 2022 \& Mar 2021 --- Aug 2021}
{Shatin Pui Ying College}
\begin{itemize}[leftmargin=1.2cm]
    \item Authored multiple-choice question templates for the HKDSE Mathematics and Physics syllabuses.
    \item Programmed in a custom external domain-specific language based on JavaScript and KaTeX.
    \item Used such meta-language to generate HTML code, mathematical tables, graphs, and 3D graphics.
    \item Participated in the development of the language.
\end{itemize}

\jobTitle
{Fullstack Developer}
{Jun 2022 --- Aug 2022}
{Shatin Pui Ying College}
\begin{itemize}[leftmargin=1.2cm]
    \item Developed an electronic ticketing system for the school Musical.
    \begin{itemize}
        \item Semi-automated order management, seat arrangement, mission control, and bulk e-mailing.
        \item Admission via QR code.
    \end{itemize}
    \item Developed a series of timetable scheduling web apps for exams, lessons, and HKDSE invigilation.
\end{itemize}

\jobTitle
{Student Teaching Assistant --- ENGG1340 Computer Programming II}
{Jan 2022 --- Jun 2022}
{The University of Hong Kong}
\begin{itemize}[leftmargin=1.2cm]
    \item Tutored a class of 85 in topics:
    \begin{itemize}
        \item Advanced Python programming.
        \item Linux shell commands.
        \item Shell scripts.
        \item C/C++ programming.
        \item Separate compilation techniques.
    \end{itemize}
    \item Hosted weekly lab sessions.
    \item Reviewed assignments according to a marking scheme.
    \item Guided discussions on Moodle.
\end{itemize}

\jobTitle
{Student Teaching Assistant --- ENGG1330 Computer Programming I}
{Sep 2021 --- Dec 2021}
{The University of Hong Kong}
\begin{itemize}[leftmargin=1.2cm]
    \item Tutored a class of 45 in topics:
    \begin{itemize}
        \item Python programming.
        \item Searching and sorting algorithms.
    \end{itemize}
    \item Hosted weekly lab sessions.
    \item Reviewed assignments according to a marking scheme.
    \item Guided discussions on Ed.
    \item Gave individual video feedback on coursework.
\end{itemize}

\section{EDUCATION}

\jobTitle
{Bachelor of Engineering in Computer Science}
{Sep 2020 --- Jan 2024}
{The University of Hong Kong}
\begin{itemize}[leftmargin=1.2cm]
    \item Focus: Theoretical Computer Science
\end{itemize}

\jobTitle
{International Exchange}
{Jan 2023 --- Jun 2023}
{Royal Holloway, University of London}
\begin{itemize}[leftmargin=1.2cm]
    \item School of Engineering, Physical and Mathematical Sciences.
    \item Courses from Department of Computer Science.
\end{itemize}

\jobTitle
{Secondary Education --- Hong Kong Diploma of Secondary Education}
{Sep 2013 --- Jun 2020}
{Shatin Pui Ying College}
\begin{itemize}[leftmargin=1.2cm]
    \item First in Information and Communications Technology in final year.
    \item Third in Physics in final year.
\end{itemize}

\section{CERTIFICATIONS}

\jobTitle
{IELTS Academic}
{May 2022}
{Overall 7.5}

\jobTitle
{TOEIC Listening \& Reading Test}
{Jun 2018}
{Overall 925}

\jobTitle
{ABRSM Practical Piano Grade 7}
{2011}
{Distinction}

\jobTitle
{ABRSM Music Theory Grade 5}
{2010}
{Pass}



\end{document}
