\resumeSubHeadingListStart

\resumeSubItem{CIFAR10-HOG-PCA-SVM (Machine Learning, Computer Vision)}{

Image classifier for the CIFAR-10 dataset. 62\% accuracy without deep neural network or convolutional kernels. Feature extraction via Histogram of Oriented Gradients. Dimensionality reduction via Grayscaling, HOG, and Principal Component Analysis. Support Vector Machine with the radial basis function kernel. 5 minutes to train. (Dec 2022)
}

\resumeSubItem{Parallel Samplesort (Multi-threading, Semaphore, Mutex lock)}{

Mutli-threaded Samplesort with arbitrary number of threads. Sorts $10^8$ integers in 5 seconds with 16 threads. (Nov 2022)
}

\resumeSubItem{3230shell (Operating System, Linux)}{

Linux shell which supports command parsing, program execution, signals handling, multiple background processes, arbitrary number of piped processes and process statistics in any combinations. (Oct 2022)
}

\resumeSubItem{Enoch BRC (Fullstack, PWA, Static Site)}{

Bible reading challenge Progressive Web App tailored made for a church. Readers read 8 chapters weekly to finish all 1189. Includes leader-board and progress tracker. (In production since Oct 2022)}

\resumeSubItem{CMM (Cryptocurrency, Algorithmic trading, Cloud Computing, Data Science)}{

Back-testing suite for ALGOGENE Algo Crypto Trading Challenge 2022 (Global). Market pattern detection and alert via web-hook. Involves APIs of Trading View, Binance, Alpaca, Google Cloud, and Discord. (Jointly developed Oct 2022)}

\resumeSubItem{WinMaths (Software Language, Code Generation, Functional Programming, Typesetting)}{

A custom domain-specific external meta-language based on JavaScript and KaTeX, which generates random Mathematics and Physics multiple-choice questions together with the neccessary typesetted tables, graphs, and 3D graphics. Runs as a fullstack web app, serving hundreds of students daily. Mentioned in \href{https://std.stheadline.com/smartparents/article/2572/}{Sing Tao Daily's Weekly Education article no. 610}. (Jointly developed with Debater Mok and in production since 2019)}

\resumeSubItem{HackOS (Unity, Cyber-security)}{

Offensive cyber-security simulator game. Sandbox experience with pruned replicas of nmap, ssh, hydra, and an array of UNIX-like commands. (May 2022)}

\resumeSubItem{RNA Fighter (Game)}{

Terminal puzzle-solving game with colored text user-interface. Type RNA sequences to defuse viruses. Includes text-based dialogues, scroll view, page navigation, and in-place buffer update. Built with Ncurses and C++. (May 2021)}

\resumeSubItem{Duckietown (Computer Vision, Reinforcement Learning, Self-driving)}{

Simulated self-driving for Duckietown with Deep Deterministic Policy Gradient with Actor \& Critic networks. (Dec 2020)}

\resumeSubItem{Bubble Sheet OMR (E-learning, OMR)}
{

GUI program written in Qt to detect MCQ options given a bubble sheet pdf. Coordinates can be exported for automatic marking purpose. Supports fully automatic detection, and fine manual adjustments. Multi-threaded. (Jun 2019)}

\resumeSubItem{Real-time Room Status System (Fullstack, RFID)}{

Developed and used for STEM Camp 2018 \& 2019 at Shatin Pui Ying College. Students from 16 primary schools could view booth/room statuses on iPads, and check in \& out by tapping RFID cards. (Apr 2019)}


\resumeSubItem{SLMS (Database, GUI)}{

School Library Management System. Developed with Qt and SQLite, a GUI program that provides CRUD functionalities to common library administration, such as book categorization, borrow/return management, mass book record import, barcode scanning, and overdue alert. Object-oriented and separately compiled. (May 2019)}


\resumeSubItem{Contact List Manager}{

Terminal contact manager with colored text user-interface. Provides CRUD functionalities to manage contacts with multiple fields. Uses hashing algorithms for authentication. Built with Windows API and C++. (May 2018)}

\resumeSubHeadingListEnd

